---
title: "Sister vs Cousin Cocktail Investigation"
author: "Script by Alisha Monsibais, wetlab by Alisha and Olivia (7/22/22) "
date: '2024-07-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Project Summary 
Bacteria was plated on a 96 well plate and exposed to the following phage: ANB28, KB824, SBP2phi2, SBP4phi1, SBP5phi1. Three were mixed into a similar phage cocktial SBP2phi2, SBP4phi1 and SBP5phi1, while three were mixed into a genetically distint phage cocktail, ANB28, KB824, and SBP2phi2. 

This was ran on the molecular device plate reader at OD600 for 72 hours at 37C. 
Date: 7/22/22

## 1. Exploratory Data Analysis 
```{r loading packages, message=FALSE, warning=FALSE, include=FALSE}
library(knitr) #nice table output 
library(tidyverse)
library(reshape2) #helps melt data - data wrangling 
library(ggpubr)
library(dplyr)
library(gcplyr) #AUC function 


library(ggplot2)
library(viridis)

```

```{r loading in data}
#MOL DIA - RT - (SI: 250) 
rep37<- read.delim("220722_Eco_Cocktail_rep1.1.txt", header = FALSE, sep = "\t", skip = 2)

```

```{r}
########MOL DIA Formatting (SI : 319) MOI 0.2 and 1.0 ###########
#More formatting - 37C (SI : 319)
names(rep37) = rep37[1,] #duplicates row 1 into row names
rep37 = rep37[-1,] #removes row 1
rep37 = rep37[,-2] #removed column 2 (temp log)
names(rep37)[1] <- "Time" #Relabels Time(HH:MM:SS) to just Time
#removed the bottom two lines to only have data - data include "~end and file name"
rep37 <- slice(rep37, 1:(n()-2))

Time <- rep37[,1] #makes vector time character string
Time <- Time[-c(1:4)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:15:00","00:30:00","00:45:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 

#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
rep37$Time <- NULL #removes Time column in data frame
rep37 <- cbind(Time, rep37) #adds new Time column to data frame with correct time format

#########  Reformat the Data  #########

#Reshaping the data
t_rep37 <- melt(rep37, id=("Time"), variable.name="Well", value.name = "OD600") 

#Changes the OD reading from character to numeric 
t_rep37$OD600 <- as.numeric(as.character(t_rep37$OD600))

#To view the summary of the data
summary(t_rep37)
head(t_rep37)
```



```{r loading in maps}
#########  Annotate the Data  #########

#Retrieving the map to annotated the Data
platemap<- read.csv("220722_Eco_Cocktail_map.csv")

#Viewing the map
head(platemap)

#The data will be reshaped and paired by Wells with the use of Inner_join (dplyr)
rep37_annotated <- inner_join(t_rep37, platemap, by = "Well")

```


```{r forloop for Data wrangling}

rep37_96well <- ggplot(rep37_annotated, aes(x=Time, y=OD600, color = Bacteria))+
  ggtitle("STM vs Individual Phage and Cocktails ", subtitle = "Rep 1 - MOI 1 - 37C") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=20, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"))+
  theme(plot.title = element_text(hjust = 0.5))+
  facet_grid(Letter~Column) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
#Shows graph
rep37_96well


```

```{r Synergy Plate}
rep37_annotated 

Cocktail_data <- rep37_annotated %>%
   filter(Time <= 40) %>%
   filter(Phage %in% c("Sister", "Cousin", "SM")) %>%
   filter(Bacteria != "Media") %>%
   mutate(Phage = recode(Phage, 
                         "SM" = "Bacteria Control", 
                         "Sister" = "Similar Cocktail", 
                         "Cousin" = "Distinct Cocktail"))

ggplot(Cocktail_data, aes(x=Time, y = OD600, color = Phage)) +
  geom_line() +
  scale_color_manual(values = c("black","firebrick1", "slateblue4"))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 30)) +
  xlab("Time (hours)") + ylab("OD600") +
  facet_wrap( ~ Bacteria, ncol=3) +
  theme(strip.text.x = element_text(size = 20)) +
  theme_linedraw()


AUC_results_1 <- rep37_annotated %>%
  group_by(Well) %>%
  mutate(Time = round(Time, 1)) %>%
  summarise(AUC = auc(y=OD600, x=Time)) %>%
  ungroup() %>%
  inner_join(platemap, by='Well') %>%
  filter(Bacteria != "Media") %>%
  filter(Phage %in% c("Sister", "Cousin", "SM")) %>%
  mutate(Phage = recode(Phage, 
                         "SM" = "Bacteria Control", 
                         "Sister" = "Similar Cocktail", 
                         "Cousin" = "Distinct Cocktail"))

cocktail.lm <- lm(AUC ~ Phage, data = AUC_results_1)
cocktail.av <- aov(cocktail.lm)
cocktail_anova_table <- anova(cocktail.av)
write.csv(cocktail_anova_table, file = "Cocktail_anova_table.csv")
 
library(broom)
library(knitr)

cocktail.posthoc <- TukeyHSD(cocktail.av)
tidy(cocktail.posthoc) %>% knitr::kable()
cocktail_HSD_table <- tidy(cocktail.posthoc)
write.csv(cocktail_HSD_table, file = "cocktail_HSD_table.csv")

library(report) 

report(cocktail.av)

```


```{r}

Violin <- AUC_results_1  %>%
  ggplot(aes(x=Phage, y=AUC, fill = Phage)) + 
  geom_violin(trim = TRUE) +  # Trimming the violins to the data range
  scale_fill_manual(values=c("gray69", "firebrick3", "slateblue4")) +
   geom_jitter(position = position_jitter(width = 0.2, height = 0), size = 1.2, alpha = 0.7) + 
  labs(y = "AUC", x = NULL) +
  ggtitle("Area Under the Curve of STM Strains \n after 40 Hours with Differing Phage Cocktails") +
  theme_linedraw() +
  ylim(0,110)+
  theme(
    plot.title = element_text(size = 20, hjust = 0.5, face = "bold"),
    axis.title.x = element_text(size = 15, face = "bold"),
    axis.title.y = element_text(size = 15, face = "bold"), 
    axis.text.x = element_text(size = 12), 
    axis.text.y = element_text(size = 12), 
    legend.position = "none") +
  stat_compare_means(method = "anova", label.y = 0) 

Violin
ggsave("SisterVSCousin.png", plot = Violin, device = "png", width = 7, height = 5)





```

```{r Sister vs Cousin Genetic info}

viridic_sister <- read.delim("Sister_VIRIDIC_sim-dist_table.tsv",header = T,sep = '\t')
viridic_cousin <- read.delim("Cousin_VIRIDIC_sim-dist_table.tsv",header = T,sep = '\t')



vir.corr.sister <- viridic_sister %>%
  rename("SBP5Φ1" = "SBP5phi1", 
         "SBP4Φ1" = "SBP4phi1") %>%
  mutate(genome = case_when(
    genome == "SBP5phi1" ~ "SBP5Φ1",
    genome == "SBP4phi1" ~ "SBP4Φ1",
    TRUE ~ as.character(genome)))

vir.corr.cousin <- viridic_cousin %>%
  rename("SBP2Φ2" = "SBP2phi2") %>%
  mutate(genome = case_when(
    genome == "SBP2phi2" ~ "SBP2Φ2",
    TRUE ~ as.character(genome)))


#sister
vir.melt.sister <- melt(vir.corr.sister, id.vars = "genome")
rownames(vir.corr.sister) <- vir.corr.sister[,1]
clusters_s <- hclust(dist(vir.corr.sister[,-1]))
clusters_2_s <- hclust(dist(t(vir.corr.sister[,-1])))
clusters.order_s <- clusters_2_s$labels[clusters_2_s$order]

#Order for re-organize data
cat(clusters.order_s)



vir.melt.sister$variable <- factor(vir.melt.sister$variable, ordered=T, levels= clusters.order_s, 
                            labels= c("SBP5Φ1", "KB824" , "SBP4Φ1"))
vir.melt.sister$genome <- factor(vir.melt.sister$genome, ordered=T, levels= clusters.order_s, 
                       labels= c("SBP5Φ1", "KB824" , "SBP4Φ1"))


Sister <- ggplot(data = vir.melt.sister) +
  theme_blank()+
  geom_tile(aes(x=genome, y=variable, fill=value), color="black") +
  labs(fill="", x='',y='') +
  geom_text(aes(x=genome, y=variable, label = round(value, digits = 2))) +
  scale_fill_gradientn(colors = c("#ffffb2", '#00d400','#00a300','#004100'),  breaks= c(70,9,95,100),labels=c("70 %", "90 %","95 %","100 %"), limits=c(70,100),
                       na.value = "white") +
  theme(axis.text = element_text(size=15, color="black"),
    axis.text.x = element_text(angle=90, hjust = 1, vjust = 0.5),
    legend.text = element_text(size=10),
    legend.key.size = unit(x = 10, units = "mm")) + coord_fixed(ratio = 1) 

ggsave("VIRDIC_heatmap_sister.pdf", plot = Sister, width = 6, height = 6, units = "in", dpi = 1200)


theme_blank <- function(...) {
  ret <- theme_bw(...)
  ret$line <- element_blank()
  ret$rect <- element_blank()
  ret$strip.text <- element_blank()
  ret$axis.text <- element_blank()
  ret$plot.title <- element_blank()
  ret$axis.title <- element_blank()
  ret$plot.margin <- structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit")
  ret
}

#cousint
vir.melt.cousin <- melt(vir.corr.cousin, id.vars = "genome")
rownames(vir.corr.cousin) <- vir.corr.cousin[,1]
clusters_c <- hclust(dist(vir.corr.cousin[,-1]))
clusters_2_c <- hclust(dist(t(vir.corr.cousin[,-1])))
clusters.order_c <- clusters_2_c$labels[clusters_2_c$order]

#Order for re-organize data
cat(clusters.order_c)

vir.melt.cousin$variable <- factor(vir.melt.cousin$variable, ordered=T, levels= clusters.order_c, 
                            labels= c("KB824", "ANB28", "SBP2Φ2"))
vir.melt.cousin$genome <- factor(vir.melt.cousin$genome, ordered=T, levels= clusters.order_c, 
                       labels= c("KB824", "ANB28", "SBP2Φ2"))


cousin <- ggplot(data = vir.melt.cousin) +
  theme_blank()+
  geom_tile(aes(x=genome, y=variable, fill=value), color="black") +
  labs(fill="", x='',y='') +
  geom_text(aes(x=genome, y=variable, label = round(value, digits = 2))) +
  scale_fill_gradientn(colors = c("#ffffb2", '#00d400','#00a300','#004100'),  breaks= c(70,9,95,100),labels=c("70 %", "90 %","95 %","100 %"), limits=c(70,100),
                       na.value = "white") +
  theme(axis.text = element_text(size=15, color="black"),
    axis.text.x = element_text(angle=90, hjust = 1, vjust = 0.5),
    legend.text = element_text(size=10),
    legend.key.size = unit(x = 10, units = "mm")) + coord_fixed(ratio = 1) 

ggsave("VIRDIC_heatmap_cousin.pdf", plot = cousin, width = 6, height = 6, units = "in", dpi = 1200)





```

