---
title: "Host Range Analysis - Set 2"
author: "Alisha Monsibais"
date: '2023-07-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "~/Desktop/230718_Host", 
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Project Summary 
STM strains (16) were grown to log phage OD600 of 0.1 and subjected to phage infection of ANB28, SBP2@2, KB824, and three phage cocktails at the following MOIs 0.001. Bacteria and phage lysates were aliqoute in a 96 well plate and read in the Aligent LogPhase 600 for 72 hours, at 37C, no shaking, 10 minute intervals

## 1. Data Cleaning and Quality Control Check 
```{r loading packages, message=FALSE, warning=FALSE, include=FALSE}
library(knitr) #nice table output 
library(tidyverse)
library(reshape2) #helps melt data - data wrangling 
library(ggpubr)
library(growthcurver) #growth curve package 
library(ggbreak) #ggarrange 
library(broom)
library(dplyr)
library(lmerTest)
library(sjPlot)
library(rstatix) #pipefriendly stats 
library(emmeans)
```

```{r loading in data}
#Set Wd
Curve1 <- read.csv("230728_HostRange_Set2_MOI1_plate1.csv")
Curve2 <- read.csv("230728_HostRange_Set2_MOI1_plate2.csv")
Curve3 <- read.csv("230728_HostRange_Set2_MOI1_plate3.csv")
Curve4 <- read.csv("230728_HostRange_Set2_MOI1_plate4.csv")
```

```{r loading in maps}
platemap1 <- read.csv("230728_Plate1_map.csv")
platemap2 <- read.csv("230728_Plate2_map.csv")
platemap3 <- read.csv("230728_Plate3_map.csv")
platemap4 <- read.csv("230728_Plate4_map.csv")

```


```{r Data wragling, message=FALSE, warning=FALSE, include=FALSE}
##### Fix Data for MTC #####
#Rep 1
Time <- Curve1[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve1$Time <- NULL #removes Time column in data frame
Curve1 <- cbind(Time, Curve1) #adds new Time column to data frame with correct time format

#Rep 2
Time <- Curve2[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve2$Time <- NULL #removes Time column in data frame
Curve2 <- cbind(Time, Curve2) #adds new Time column to data frame with correct time format

#Rep 3
Time <- Curve3[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve3$Time <- NULL #removes Time column in data frame
Curve3 <- cbind(Time, Curve3) #adds new Time column to data frame with correct time format

#Rep 4
Time <- Curve4[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve4$Time <- NULL #removes Time column in data frame
Curve4 <- cbind(Time, Curve4) #adds new Time column to data frame with correct time format

#####Melt Data#####

C1_melt <- melt(Curve1, id=("Time"), variable.name= "Well", value.name = "OD600")
C1_melt$OD600 <- as.numeric(as.character(C1_melt$OD600)) #changes OD to numeric

C2_melt <- melt(Curve2, id=("Time"), variable.name= "Well", value.name = "OD600")
C2_melt$OD600 <- as.numeric(as.character(C2_melt$OD600)) #changes OD to numeric

C3_melt <- melt(Curve3, id=("Time"), variable.name= "Well", value.name = "OD600")
C3_melt$OD600 <- as.numeric(as.character(C3_melt$OD600)) #changes OD to numeric

C4_melt <- melt(Curve4, id=("Time"), variable.name= "Well", value.name = "OD600")
C4_melt$OD600 <- as.numeric(as.character(C4_melt$OD600)) #changes OD to numeric
```

```{r annotating data from plate map, message=FALSE, warning=FALSE, include=FALSE}

Cannotated1 <- inner_join(C1_melt, platemap1, by='Well')
Cannotated2 <- inner_join(C2_melt, platemap2, by='Well')
Cannotated3 <- inner_join(C3_melt, platemap3, by='Well')
Cannotated4 <- inner_join(C4_melt, platemap4, by='Well')
```

```{r Plotting 96 well plate to check QC parameters, echo=FALSE, message=FALSE, warning=FALSE}

#Graphing in 96 well format to check plate bias or issues with potential contamination. 
png("Figures/230728_Set2_plate1.png", units="in", width=10, height=6, res=600)
C1 <- ggplot(Cannotated1, aes(x=Time, y=OD600, color = Strain, linetype = Phage ))+
  ggtitle("Set 2 - Plate 1") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Number) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C1
dev.off()

png("Figures/230728_Set2_plate2.png", units="in", width=10, height=6, res=600)
C2 <- ggplot(Cannotated2, aes(x=Time, y=OD600, color = Strain, linetype = Phage ))+
  ggtitle("Set 2 - Plate 2") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Number) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C2
dev.off()

png("Figures/230728_Set2_plate3.png", units="in", width=10, height=6, res=600)
C3 <- ggplot(Cannotated3, aes(x=Time, y=OD600, color = Strain, linetype = Phage ))+
  ggtitle("Set 2 - Plate 3") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Number) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C3
dev.off()

png("Figures/230728_Set2_plate4.png", units="in", width=10, height=6, res=600)
C4 <- ggplot(Cannotated1, aes(x=Time, y=OD600, color = Strain, linetype = Phage ))+
  ggtitle("Set 2 - Plate 4") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Number) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C4
dev.off()

Plate_96 <- ggarrange(C1, C2, C3, C4,
                      labels = c("A", "B", "C", "D"),
                      #ncol = 1, nrow = 4, 
                      common.legend = TRUE, legend = "right")
Plate_96



```



```{r AUC - 12 Hours}

C1_12 <- Cannotated1 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,12.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


C2_12 <- Cannotated2 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,12.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


C3_12 <- Cannotated3 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,12.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 
   
C4_12 <- Cannotated4 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,12.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


#Combinds all the data 
Set2.12 <- C1_12 %>%
  union_all(C2_12) %>%
  union_all(C3_12) %>%
  union_all(C4_12) %>%
  filter(Strain != "B28B") #B28B was in first set 


```
## Plot 12 hour Data 

```{r plotting}
png("Figures/230728_heapmap_auc_12hours.png", units="in", width=12, height=6, res=1200)
Set2.12 %>%
  mutate(name = fct_relevel(Phage, "Cocktail", "SBP2Φ2", "KB824", "ANB28", "Bacteria")) %>%
  ggplot(aes(Strain, name, fill= growthpercent)) + 
  theme_blank() + geom_tile(color="black", size = 0.25) +
  ggtitle("Set 1 - Area Under the Curve - 12 Hours") +
  labs(fill = 'Growth %')+ ylab("Phage Input")+
  scale_fill_gradient2(low="white", high="#EF2402") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10),
        axis.title.x = element_text(color = "black", size = 12, face = "bold"), 
        axis.title.y = element_text(color = "black", size = 12, face = "bold")) 
dev.off()
```

```{r AUC - 20 Hours}

C1_20 <- Cannotated1 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,20.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


C2_20 <- Cannotated2 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,20.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


C3_20 <- Cannotated3 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,20.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 
   
C4_20 <- Cannotated4 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,20.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


#Combinds all the data 
Set2.20 <- C1_20 %>%
  union_all(C2_20) %>%
  union_all(C3_20) %>%
  union_all(C4_20) %>%
  filter(Strain != "B28B") #B28B was in first set 


```


## Plot 20 hour Data 

```{r plotting}
png("Figures/230728_heapmap_auc_20hours.png", units="in", width=12, height=6, res=1200)
Set2.20 %>%
  mutate(name = fct_relevel(Phage, "Cocktail", "SBP2Φ2", "KB824", "ANB28", "Bacteria")) %>%
  ggplot(aes(Strain, name, fill= growthpercent)) + 
  theme_blank() + geom_tile(color="black", size = 0.25) +
  ggtitle("Set 1 - Area Under the Curve - 20 Hours") +
  labs(fill = 'Growth %')+ ylab("Phage Input")+
  scale_fill_gradient2(low="white", high="#EF2402") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10),
        axis.title.x = element_text(color = "black", size = 12, face = "bold"), 
        axis.title.y = element_text(color = "black", size = 12, face = "bold")) 
dev.off()
```


```{r AUC - 12 Hours}

C1_40 <- Cannotated1 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,40.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


C2_40 <- Cannotated2 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,40.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


C3_40 <- Cannotated3 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,40.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 
   
C4_40 <- Cannotated4 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,40.0)) %>%
  filter(Phage %in% c("sm", "ANB28", "KB824", "SBP2_2", "3C", "media+SM")) %>%
  mutate(Phage = case_when(
  Phage == "3C" ~ "Cocktail",
  Phage == "SBP2_2" ~ "SBP2Φ2",
  Phage == "sm" ~ "Bacteria",
  Phage == "media+SM" ~ "Blank",
  TRUE ~ as.character(Phage))) %>%
  group_by(Phage, Strain) %>%
  summarise(uncorrected_auc = auc(y = OD600, x = as.numeric(Time))) %>%
  ungroup() %>%
  mutate(blank = uncorrected_auc[Phage =='Blank']) %>% filter(Phage != "Blank") %>%
  mutate(auc = uncorrected_auc - blank) %>%
  group_by(Strain) %>%
  mutate(AvgBac_AUC = auc[Phage =='Bacteria']) %>%
  mutate(growthpercent = (1-(AvgBac_AUC - auc)/AvgBac_AUC)*100) 


#Combinds all the data 
Set2.40 <- C1_40 %>%
  union_all(C2_40) %>%
  union_all(C3_40) %>%
  union_all(C4_40) %>%
  filter(Strain != "B28B") #B28B was in first set 


```
```{r plotting}
png("Figures/230728_heapmap_auc_40hours.png", units="in", width=12, height=6, res=1200)
Set2.40 %>%
  mutate(name = fct_relevel(Phage, "Cocktail", "SBP2Φ2", "KB824", "ANB28", "Bacteria")) %>%
  ggplot(aes(Strain, name, fill= growthpercent)) + 
  theme_blank() + geom_tile(color="black", size = 0.25) +
  ggtitle("Set 1 - Area Under the Curve - 40 Hours") +
  labs(fill = 'Growth %')+ ylab("Phage Input")+
  scale_fill_gradient2(low="white", high="#EF2402") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10),
        axis.title.x = element_text(color = "black", size = 12, face = "bold"), 
        axis.title.y = element_text(color = "black", size = 12, face = "bold")) 
dev.off()
```


##Combind Data 

```{r}

#previous data from set 1
Set1.12 <- read.csv("230721_cleanauc_Set1.12.csv")
Set1.20 <- read.csv("230721_cleanauc_Set1.20.csv")
Set1.40 <- read.csv("230721_cleanauc_Set1.40.csv")

Combined_12hours <-  Set1.12 %>%
  union_all(Set2.12)

Combined_20hours <-  Set1.20 %>%
  union_all(Set2.20)

Combined_40hours <-  Set1.40 %>%
  union_all(Set2.40)

write.csv(Combined_12hours,file='All_cleanauc.12.csv', row.names=FALSE)
write.csv(Combined_20hours,file='All_cleanauc.20.csv', row.names=FALSE)
write.csv(Combined_40hours,file='All_cleanauc.40.csv', row.names=FALSE)

png("Figures/Combined_Set1_Set2_12hours_auc.png", units="in", width=12, height=6, res=1200)
Combined_12hours %>%
  mutate(name = fct_relevel(Phage, "Cocktail", "SBP2Φ2", "KB824", "ANB28", "Bacteria")) %>%
  ggplot(aes(Strain, name, fill= growthpercent)) + 
  theme_blank() + geom_tile(color="black", size = 0.25) +
  ggtitle("Area Under the Curve for 12 Hours") + labs(fill = 'Growth %')+ ylab("Phage Input")+
  scale_fill_gradient2(low="white", high="#EF2402", midpoint = 0) + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10),
        axis.title.x = element_text(color = "black", size = 12, face = "bold"), 
        axis.title.y = element_text(color = "black", size = 12, face = "bold")) 
dev.off()

png("Figures/Combined_Set1_Set2_20hours_auc.png", units="in", width=12, height=6, res=1200)
Combined_20hours %>%
  mutate(name = fct_relevel(Phage, "Cocktail", "SBP2Φ2", "KB824", "ANB28", "Bacteria")) %>%
  ggplot(aes(Strain, name, fill= growthpercent)) + 
  theme_blank() + geom_tile(color="black", size = 0.25) +
  ggtitle("Area Under the Curve for 20 Hours") + labs(fill = 'Growth %')+ ylab("Phage Input")+
  scale_fill_gradient2(low="white", high="#EF2402", midpoint = 0) + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10),
        axis.title.x = element_text(color = "black", size = 12, face = "bold"), 
        axis.title.y = element_text(color = "black", size = 12, face = "bold")) 
dev.off()

png("Figures/Combined_Set1_Set2_24hours_auc.png", units="in", width=12, height=6, res=1200)
Combined_40hours %>%
  mutate(name = fct_relevel(Phage, "Cocktail", "SBP2Φ2", "KB824", "ANB28", "Bacteria")) %>%
  ggplot(aes(Strain, name, fill= growthpercent)) + 
  theme_blank() + geom_tile(color="black", size = 0.25) +
  ggtitle("Area Under the Curve for 40 Hours") + labs(fill = 'Growth %')+ ylab("Phage Input")+
  scale_fill_gradient2(low="white", high="#EF2402", midpoint = 0) + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1,color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10),
        axis.title.x = element_text(color = "black", size = 12, face = "bold"), 
        axis.title.y = element_text(color = "black", size = 12, face = "bold")) 
dev.off()
```


