---
title: "MOI for B28B - Manuscript 1 - Figure 5 and 6"
author: "Alisha Monsibais"
date: '2023-01-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Project Summary 
B28B was grown to log phage OD600 of 0.1 and subjected to phage infection of ANB28, SBP2@2, KB824, two phage and three phage cocktails and the following MOIs 0.001, 1, 10. Bacteria and phage lysates were aliqoute in a 96 well plate and read in the Aligent LogPhase 600. 

## 1. Exploratory Data Analysis 
```{r loading packages, message=FALSE, warning=FALSE, include=FALSE}
library(knitr) #nice table output 
library(tidyverse)
library(reshape2) #helps melt data - data wrangling 
library(ggpubr)
library(growthcurver) #growth curve package 
library(ggbreak) #ggarrange 
library(broom)
library(dplyr)
library(lmerTest)
library(sjPlot)
library(rstatix) #pipefriendly stats 
library(emmeans)
library(report) 
```

```{r loading in data}
Curve1 <- read.csv("../Raw_data/230120_MOI_0.001_1_10_B28B_rep1.csv")
Curve2 <- read.csv("../Raw_data/230120_MOI_0.001_1_10_B28B_rep2.csv")
Curve3 <- read.csv("../Raw_data/230120_MOI_0.001_1_10_B28B_rep3.csv")
Curve4 <- read.csv("../Raw_data/230120_MOI_0.001_1_10_B28B_rep4.csv")
```

```{r loading in maps}
platemap <- read.csv("230120_platemap.csv")
```


```{r Data wragling, message=FALSE, warning=FALSE, include=FALSE}
##### Fix Data for MTC #####
#
Time <- Curve1[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve1$Time <- NULL #removes Time column in data frame
Curve1 <- cbind(Time, Curve1) #adds new Time column to data frame with correct time format

#Rep 2
Time <- Curve2[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve2$Time <- NULL #removes Time column in data frame
Curve2 <- cbind(Time, Curve2) #adds new Time column to data frame with correct time format

#Rep 3

Time <- Curve3[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve3$Time <- NULL #removes Time column in data frame
Curve3 <- cbind(Time, Curve3) #adds new Time column to data frame with correct time format

#Rep 4

Time <- Curve4[,1] #makes vector time character string
Time <- Time[-c(1:6)] #removed 1-6 because format is incorrect
fix <- c("00:00:00","00:10:00","00:20:00", "00:30:00", "00:40:00", "00:50:00") #fixes format
Time <- append(fix, Time, after = length(fix)) #appends 
#Change vector of Time from HH:MM:SS to numeric hour format
Time <- sapply(strsplit(Time, ":"), function(x) {
  x <- as.numeric(x); x[1] + x[2]/60 + x[3]/3600
})
Curve4$Time <- NULL #removes Time column in data frame
Curve4 <- cbind(Time, Curve4) #adds new Time column to data frame with correct time format

#####Melt Data#####

C1_melt <- melt(Curve1, id=("Time"), variable.name= "Well", value.name = "OD600")
C1_melt$OD600 <- as.numeric(as.character(C1_melt$OD600)) #changes OD to numeric

C2_melt <- melt(Curve2, id=("Time"), variable.name= "Well", value.name = "OD600")
C2_melt$OD600 <- as.numeric(as.character(C2_melt$OD600)) #changes OD to numeric

C3_melt <- melt(Curve3, id=("Time"), variable.name= "Well", value.name = "OD600")
C3_melt$OD600 <- as.numeric(as.character(C3_melt$OD600)) #changes OD to numeric

C4_melt <- melt(Curve4, id=("Time"), variable.name= "Well", value.name = "OD600")
C4_melt$OD600 <- as.numeric(as.character(C4_melt$OD600)) #changes OD to numeric
```

```{r annotating data from plate map, message=FALSE, warning=FALSE, include=FALSE}
#annotated data with plate map information 
Cannotated1 <- inner_join(C1_melt, platemap, by='Well')
Cannotated2 <- inner_join(C2_melt, platemap, by='Well')
Cannotated3 <- inner_join(C3_melt, platemap, by='Well')
Cannotated4 <- inner_join(C4_melt, platemap, by='Well')
```

```{r Plotting 96 well plate to check QC parameters, echo=FALSE, message=FALSE, warning=FALSE}

#Graphing in 96 well format to check plate bias or issues with potential contamination. 
C1 <- ggplot(Cannotated1, aes(x=Time, y=OD600, color = Condition, linetype = MOI))+
  ggtitle("MOI Growth Curve with B28B", 
          subtitle = "Rep 1") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Row) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C1

C2 <- ggplot(Cannotated2, aes(x=Time, y=OD600, color = Condition, linetype = MOI))+
  ggtitle("MOI Growth Curve with B28B", 
          subtitle = "Rep 2") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Row) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C2

C3 <- ggplot(Cannotated3, aes(x=Time, y=OD600, color = Condition, linetype = MOI))+
  ggtitle("MOI Growth Curve with B28B", 
          subtitle = "Rep 3") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Row) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C3

C4 <- ggplot(Cannotated4, aes(x=Time, y=OD600, color = Condition, linetype = MOI))+
  ggtitle("MOI Growth Curve with B28B", 
          subtitle = "Rep 4") +
  geom_line() +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme(
    plot.title = element_text(size=12, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=9, face="bold"),
    axis.title.y = element_text(size=9, face="bold"), 
    axis.text.x = element_text(size=5), 
    axis.text.y = element_text(size=5))+
  facet_grid(Letter~Row) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
C4


png('Figures/96Well_Overview.png', units="in", width=10, height=5, res=600)
Plate_96 <- ggarrange(C1, C2, C3, C4,
                      labels = c("A", "B", "C", "D"),
                      #ncol = 1, nrow = 4, 
                      common.legend = TRUE, legend = "right")
Plate_96
dev.off()


```
## 2. Subsetting data
Data will be subsetted first for MOI difference in phages individually and graph and anova's will be run. 

```{r Subseting Data, message=FALSE, warning=FALSE, include=FALSE}
#adding the rep annotation to the data
Ca1 <- Cannotated1 %>%
  mutate(rep = 1)
Ca2 <- Cannotated2 %>%
  mutate(rep = 2)
Ca3 <- Cannotated3 %>%
  mutate(rep = 3)
Ca4 <- Cannotated4 %>%
  mutate(rep = 4)

#Combining MTC data
Data_all <- rbind(Ca2, Ca3, Ca4)
#only incorporated 3 plates - plate 1 had issue with growth 

#Need to pull BG, B28B and KB824
KB_subsetted <- Data_all %>%
  filter(Condition %in% c("B28B", "Media_SM ", "KB824")) %>%
  mutate(Time = round(Time, 1)) %>%
  mutate(MOI = str_replace(MOI, "na", "Blank"))

#Need to pull BG, B28B and KB824
SBP_subsetted <- Data_all %>%
  filter(Condition %in% c("B28B", "Media_SM ", "SBP2@2")) %>%
  mutate(Time = round(Time, 1)) %>%
  mutate(MOI = str_replace(MOI, "na", "Blank"))

#Need to pull BG, B28B and KB824
ANB_subsetted <- Data_all %>%
  filter(Condition %in% c("B28B", "Media_SM ", "ANB28")) %>%
  mutate(Time = round(Time, 1)) %>%
  mutate(MOI = str_replace(MOI, "na", "Blank"))

C3_subsetted <- Data_all %>%
  filter(Condition %in% c("B28B", "Media_SM ", "3Cocktail")) %>%
  mutate(Time = round(Time, 1)) %>%
  mutate(MOI = str_replace(MOI, "na", "Blank"))

```

```{r grouping data and summary stats, echo=FALSE, message=FALSE, warning=FALSE}
#groups data
gKB_subsetted <- group_by(KB_subsetted, Time, Condition, MOI)
gSBP_subsetted <- group_by(SBP_subsetted, Time, Condition, MOI)
gANB_subsetted <- group_by(ANB_subsetted, Time, Condition, MOI)
gC3_subsetted <- group_by(C3_subsetted, Time, Condition, MOI)

#summarizes data 
sKB_subsetted <- summarise(gKB_subsetted, N=length(OD600), Average=mean(OD600), StDev = sd(OD600))
sSBP_subsetted <- summarise(gSBP_subsetted, N=length(OD600), Average=mean(OD600), StDev = sd(OD600))
sANB_subsetted <- summarise(gANB_subsetted, N=length(OD600), Average=mean(OD600), StDev = sd(OD600))
sC3_subsetted <- summarise(gC3_subsetted, N=length(OD600), Average=mean(OD600), StDev = sd(OD600))

```

## Plot Combind Data 

```{r plotting}
# Define the desired order of MOI levels
moi_order <- c("Bacteria","0.001", "1", "10", "Blank")

# Convert MOI to a factor with the specified order
sKB_subsetted$MOI <- factor(sKB_subsetted$MOI, levels = moi_order)
sSBP_subsetted$MOI <- factor(sSBP_subsetted$MOI, levels = moi_order)
sANB_subsetted$MOI <- factor(sANB_subsetted$MOI, levels = moi_order)
sC3_subsetted$MOI <- factor(sC3_subsetted$MOI, levels = moi_order)


KB <- ggplot(sKB_subsetted, aes(x = Time, y = Average, color = MOI)) +
  geom_ribbon(aes(ymin = Average - StDev, ymax = Average + StDev), fill = "#e3e3e3", linetype = 0) +
  geom_line(size = 1.5) +
  scale_color_manual(values = c("black","mediumpurple1", "purple1", "purple4", "gray30")) +
  labs(x = "Time (Hours)\n", y = "MOI") +  # Update the y-axis label to reflect the reordering
  ggtitle("KB824") +
  theme_classic() +
  theme(
    plot.title = element_text(size = 18, hjust = 0.5, face = "bold"),
    axis.title.x = element_text(size = 10, face = "bold"),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8)
  ) +
  xlim(1, 48) + ylim(0, 1.75)

KB

ANB <- ggplot(sANB_subsetted, aes(x=Time, y=Average, color = MOI))+
  geom_ribbon(aes(ymin=Average-StDev, ymax = Average+StDev), fill = "#e3e3e3", linetype=0)+
  geom_line(size = 1.5) +
  scale_color_manual(values = c("black","mediumpurple1", "purple1", "purple4", "gray30")) +
  labs(x="Time(Hours)\n", y ="OD600nm") +
  theme_classic()+
  ggtitle("ANB28")+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8)) +
  xlim(1,48) + ylim(0,1.75)
ANB


SBP <- ggplot(sSBP_subsetted, aes(x=Time, y=Average, color = MOI))+
  geom_ribbon(aes(ymin=Average-StDev, ymax = Average+StDev), fill = "#e3e3e3", linetype=0)+
  geom_line(size = 1.5) +
  scale_color_manual(values = c("black","mediumpurple1", "purple1", "purple4", "gray30")) +
  labs(x="Time(Hours)\n", y ="OD600nm") +
  ggtitle("SBP2ɸ2")+
  theme_classic()+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8)) +
  xlim(1, 48) + ylim(0,1.75)
SBP

C3 <- ggplot(sC3_subsetted, aes(x=Time, y=Average, color = MOI))+
  ggtitle("MOI gradient of Cocktail") +
  geom_ribbon(aes(ymin=Average-StDev, ymax = Average+StDev), fill = "#e3e3e3", linetype=0)+
  geom_line(size = 1.5) +
  ggtitle("Three-Phage Cocktail") +
  scale_color_manual(values = c("black","mediumpurple1", "purple1", "purple4", "gray30")) +
  labs(x="Time(Hours)\n", y ="OD600nm") +
  theme_classic()+
  theme(
    plot.title = element_text(size=20, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8)) +
  xlim(1, 48) + ylim(0,1.75)
C3
```


```{r Statistical Analysis}
# Selecting only the first 48 hours 

#Groups data to include an average "blank" column
#First part select the first 48 hour and the second part calculated blank
C1_48 <- Curve1 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,48.0))
  
C1_blank <- C1_48 %>%
  dplyr::select(Time, B2, C2, D2) %>% 
  group_by(Time) %>% 
  mutate(blank = mean(B2, C2, D2)) %>%
  ungroup() %>%
  dplyr::select(blank) %>%
  bind_cols(C1_48,.)

C2_48 <- Curve2 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,48.0))
  
C2_blank <- C2_48 %>%
  dplyr::select(Time, B2, C2, D2) %>% 
  group_by(Time) %>% 
  mutate(blank = mean(B2, C2, D2)) %>%
  ungroup() %>%
  dplyr::select(blank) %>%
  bind_cols(C2_48,.)

C3_48 <- Curve3 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,48.0))
  
C3_blank <- C3_48 %>%
  dplyr::select(Time, B2, C2, D2) %>% 
  group_by(Time) %>% 
  mutate(blank = mean(B2, C2, D2)) %>%
  ungroup() %>%
  dplyr::select(blank) %>%
  bind_cols(C3_48,.)

C4_48 <- Curve4 %>% 
  mutate(Time = round(Time, 1)) %>%
  filter(between(Time,0.0,48.0))
  
C4_blank <- C4_48 %>%
  dplyr::select(Time, B2, C2, D2) %>% 
  group_by(Time) %>% 
  mutate(blank = mean(B2, C2, D2)) %>%
  ungroup() %>%
  dplyr::select(blank) %>%
  bind_cols(C4_48,.)

#GrowthCurve Package 
#auc_l The area under the curve of the fitted logistic equation from time 0 to time t (from doc)
#Selects the Conditions of interest and the auc_l which is defined at the area under the curve of the fitted logistic equation from time 0 to time t (from doc)

#Runs the Growthcurver package on the corrected dataset 
C1_GC <-SummarizeGrowthByPlate(
  C1_blank,
  t_trim = 0,
  bg_correct = "blank", 
  plot_fit = TRUE, 
  plot_file = "C1_plot.pdf"
)

C2_GC <-SummarizeGrowthByPlate(
  C2_blank,
  t_trim = 0,
  bg_correct = "blank", 
  plot_fit = TRUE, 
  plot_file = "C2_plot.pdf"
)

C3_GC <-SummarizeGrowthByPlate(
  C3_blank,
  t_trim = 0,
  bg_correct = "blank", 
  plot_fit = TRUE, 
  plot_file = "C3_plot.pdf"
)

C4_GC <-SummarizeGrowthByPlate(
  C4_blank,
  t_trim = 0,
  bg_correct = "blank", 
  plot_fit = TRUE, 
  plot_file = "C4_plot.pdf"
)


#rename sample to well for annotation of platemap 
C1_sum <- C1_GC %>%
  dplyr::rename(Well = sample)%>%
  right_join(platemap, ., by = "Well") %>%
  filter(Condition %in% c("B28B", "ANB28", "KB824", "SBP2@2", "3Cocktail")) %>%
  dplyr::select(Well, Condition, MOI, auc_l, auc_e, sigma, note) %>%
  mutate(rep = 1)

C2_sum <- C2_GC %>%
  dplyr::rename(Well = sample)%>%
  right_join(platemap, ., by = "Well") %>%
  filter(Condition %in% c("B28B", "ANB28", "KB824", "SBP2@2", "3Cocktail")) %>%
  dplyr::select(Well, Condition, MOI, auc_l, auc_e, sigma, note) %>%
  mutate(rep = 2)

C3_sum <- C3_GC %>%
  dplyr::rename(Well = sample) %>%
  right_join(platemap, ., by = "Well") %>%
  filter(Condition %in% c("B28B", "ANB28", "KB824", "SBP2@2", "3Cocktail")) %>%
  dplyr::select(Well, Condition, MOI, auc_l, auc_e, sigma, note) %>%
  mutate(rep = 3)

C4_sum <- C4_GC %>%
  dplyr::rename(Well = sample) %>%
  right_join(platemap, ., by = "Well") %>%
  filter(Condition %in% c("B28B", "ANB28", "KB824", "SBP2@2", "3Cocktail")) %>%
  dplyr::select(Well, Condition, MOI, auc_l, auc_e, sigma, note) %>%
  mutate(rep = 4) 

#Combinds all the data 
AUC_Tables <- C2_sum %>%
  union_all(C3_sum) %>%
  union_all(C4_sum) 

#Only plates 2, 3, 4 - plate 1 did not pass QC 

```


### Question 1: How does MOI impact the overall growth of the bacteria?

#### Hypothesis: 

1. Null hypothesis: Phage input, no matter the phage quantitiy, has the same impact on the mean of bacteria growth, measured by OD600 and calculated by area under the curve (AUC). 
  - H0: 𝞵~MOI 0.001~ = 𝞵~MOI 1~ = 𝞵~MOI 10~

2. Alternative hypothesis: The the higher the MOI of phage the better at reducing the mean of bacteria growth, measured by OD600 and calculated by AUC.
  - H1: 𝞵~MOI 0.001~  > 𝞵~MOI 1~ = 𝞵~MOI 10~

#### Variable assessment: 
- Response Variable: Area under the curve (AUC)
- Predictor Variable: MOI


##### Table 1. Summary Statistics 

```{r}
#Calculates the summary statistics 
Summarystats <- AUC_Tables %>%
  group_by(Condition, MOI) %>%
  summarise(n = length(auc_l), Median = median(auc_l), Average = mean(auc_l), SD = sd(auc_l), SE = sd(auc_l)/sqrt(length((auc_l))))

#Summary table 
kable(Summarystats)

```


#### ANOVA Assumption Checks

##### Visualize the Data and check for outliers 

```{r Check Assumptions, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = AUC_Tables) + 
  aes(x = MOI, y = auc_l) + 
  geom_boxplot() + geom_point()
#Outlier check - no outliers noted 
```

##### Normality Test of AUC of one Condition

```{r Assumption - Normality, echo=FALSE, message=FALSE, warning=FALSE}

ANBonly <- filter(AUC_Tables, Condition == "ANB28")

qqnorm(ANBonly$auc_l)
qqline(ANBonly$auc_l)

#Data is normally distributed - thus we can preform the ANOVA 

```

##### Homogeneity of Variance

```{r Assumptions - Homogeneity of variance, echo=FALSE, message=FALSE, warning=FALSE}
model <- aov(auc_l ~ MOI, data = AUC_Tables)
plot(model, 1)

```



##### Table 2. Statistical Test - One-way ANOVA 

```{r Q1: Statistical Test and Post Hoc Test, echo=FALSE, message=FALSE, warning=FALSE}

#Selecting only one condition at a time 
ANBonly <- AUC_Tables %>%
  filter(Condition %in% c("B28B", "ANB28"))
SBPonly <- AUC_Tables %>%
  filter(Condition %in% c("B28B", "SBP2@2"))
KBonly <- AUC_Tables %>%
  filter(Condition %in% c("B28B", "KB824"))
C3only <- AUC_Tables %>%
  filter(Condition %in% c("B28B", "3Cocktail"))

#ANOVA with lm function 
anb.lm <- lm(auc_l ~ MOI, data = ANBonly)
anb.av <- aov(anb.lm)
anb_anova_table <- anova(anb.av)
write.csv(anb_anova_table, file = "Stats_table/anb_anova_table.csv")

kb.lm <- lm(auc_l ~ MOI, data = KBonly)
kb.av <- aov(kb.lm)
kb_anova_table <- anova(kb.av)
write.csv(kb_anova_table, file = "Stats_table/kb_anova_table.csv")

sbp.lm <- lm(auc_l ~ MOI, data = SBPonly)
sbp.av <- aov(sbp.lm)
sbp_anova_table <- anova(sbp.av)
write.csv(sbp_anova_table, file = "Stats_table/sbp_anova_table.csv")

c3.lm <- lm(auc_l ~ MOI, data = C3only)
c3.av <- aov(c3.lm)
c3_anova_table <- anova(c3.av)
write.csv(c3_anova_table, file = "Stats_table/c3_anova_table.csv")

```
##### Table 3. Post Hoc Test 
```{r}
#Follow-up Tukey Test 
anb.posthoc <- TukeyHSD(anb.av)
tidy(anb.posthoc) %>% knitr::kable()
anb_HSD_table <- tidy(anb.posthoc)
write.csv(anb_HSD_table, file = "Stats_table/anb_HSD_table.csv")

kb.posthoc <- TukeyHSD(kb.av)
tidy(kb.posthoc) %>% knitr::kable()
kb_HSD_table <- tidy(kb.posthoc)
write.csv(kb_HSD_table, file = "Stats_table/kb_HSD_table.csv")

sbp.posthoc <- TukeyHSD(sbp.av)
tidy(sbp.posthoc) %>% knitr::kable()
sbp_HSD_table <- tidy(sbp.posthoc)
write.csv(sbp_HSD_table, file = "Stats_table/sbp_HSD_table.csv")

c3.posthoc <- TukeyHSD(c3.av)
tidy(c3.posthoc) %>% knitr::kable()
c3_HSD_table <- tidy(c3.posthoc)
write.csv(c3_HSD_table, file = "Stats_table/c3_HSD_table.csv")

```

```{r Q1: Figure, fig.cap = "**Figure 1.** One-Way ANOVA of Growth Curves via AUC. (A) Growth curves of B28B with phages ANB28, SBP2.2, and a two-phage cocktail including both. Log phase bacteria were plated in a 96-well plate, and Phages were added to the designated wells at an MOI 10. OD600 readings were collected in a Molecular Device plate reader for 72 hours at 37C with minimal shaking. (B) AUC of the Growth Curves from (A) was calculated using the Growthcurver package, and a One-way ANOVA was performed. The main effect of the Condition is statistically significant (F(3,20) = 395.58, p <0.001; 95% CI [0.97, 1.00], n=6). Tukey’s HSD Test for multiple comparisons found that all conditions are significantly different (p = <0.0001, see table for CI ranges).", echo=FALSE, message=FALSE, warning=FALSE}

anb_anova <- ANBonly  %>%
  ggplot(aes(x=factor(MOI, level=c("Bacteria", "0.001", "1", "10")), y=auc_l, fill = MOI)) + 
  geom_violin() +
  geom_jitter() +
  labs(y = "AUC", x = "MOI") +
  theme_classic()+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8), 
    legend.position = "none") +
  stat_compare_means(method = "anova", label.y = 0) +
  scale_fill_manual(values = c("mediumpurple1", "purple1", "purple4", "black")) 
anb_anova

sbp_anova <- SBPonly  %>%
  ggplot(aes(x=factor(MOI, level=c("Bacteria", "0.001", "1", "10")), y=auc_l, fill = MOI)) + 
  geom_violin() +
  geom_jitter() +
  labs(y = "AUC", x = "MOI") +
   theme_classic()+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8)) +
  stat_compare_means(method = "anova", label.y = 0) +
    scale_fill_manual(values = c("mediumpurple1", "purple1", "purple4", "black"))
sbp_anova

kb_anova <- KBonly  %>%
  ggplot(aes(x=factor(MOI, level=c("Bacteria", "0.001", "1", "10")), y=auc_l, fill = MOI)) + 
  geom_violin() +
  geom_jitter() +
  labs(y = "AUC", x = "MOI") +
  theme_classic()+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8)) +
  stat_compare_means(method = "anova", label.y = 0) +
    scale_fill_manual(values = c("mediumpurple1", "purple1", "purple4", "black")) 
kb_anova

c3_anova <- C3only  %>%
  ggplot(aes(x=factor(MOI, level=c("Bacteria", "0.001", "1", "10")), y=auc_l, fill = MOI)) + 
  geom_violin() +
  geom_jitter() +
  labs(y = "AUC", x = "MOI") +
  theme_classic()+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=10, face="bold"),
    axis.title.y = element_text(size=10, face="bold"), 
    axis.text.x = element_text(size=8), 
    axis.text.y = element_text(size=8)) +
  stat_compare_means(method = "anova", label.y = 0) +
    scale_fill_manual(values = c("mediumpurple1", "purple1", "purple4", "black"))
c3_anova


```


```{r}
png("Figures/MOI_growth_curves.png", units="in", width=10, height=6, res=600)
MOI_growthcurve <- ggarrange(ANB,KB, SBP, anb_anova, kb_anova, sbp_anova,
                      labels = c("A", "B", "C", "D", "E", "F"),
                      common.legend = TRUE, legend = "bottom", 
                      align = "h") 
MOI_growthcurve
dev.off()
```

```{r 3 Phage Cocktail Analysis}
#only running MOI 1
MOI_1_auc <- AUC_Tables %>%
  filter(MOI %in% c("1", "Bacteria")) %>%
  filter(Condition %in% c("B28B", "ANB28", "KB824", "3Cocktail", "SBP2@2")) %>%
  rename(Input = Condition) %>%
  mutate(Input = case_when(
  Input == "3Cocktail" ~ "Cocktail",
  Input == "SBP2@2" ~ "SBP2Φ2", 
  Input == "B28B" ~ "Bacteria", 
  TRUE ~ as.character(Input)))
  

#running the anvoa
moi1.lm <- lm(auc_l ~ Input, data = MOI_1_auc)
moi1.av <- aov(moi1.lm)
anova(moi1.av) %>% knitr::kable()
moi1_anova_table <- anova(moi1.av)
write.csv(moi1_anova_table, file = "Stats_table/moi1_anova_table.csv")

#running posthoc test
moi1.posthoc <- TukeyHSD(moi1.av)
tidy(moi1.posthoc) %>% knitr::kable()
moi1_HSD_table <- tidy(moi1.posthoc)
write.csv(moi1_HSD_table, file = "Stats_table/moi1_HSD_table.csv")

#Need to pullBG, B28B and KB824
MOI_1 <- Data_all %>%
  filter(MOI %in% c("1", "Bacteria")) %>%
  filter(Condition %in% c("B28B", "ANB28", "KB824", "3Cocktail", "SBP2@2")) %>%
  mutate(Time = round(Time, 1)) %>%
  rename(Input = Condition) %>%
  mutate(Input = case_when(
  Input == "3Cocktail" ~ "Cocktail",
  Input == "SBP2@2" ~ "SBP2Φ2", 
  Input == "B28B" ~ "Bacteria", 
  TRUE ~ as.character(Input)))

gMOI_1 <- group_by(MOI_1, Time, Input)

#summarizes data 
sMOI_1 <- summarise(gMOI_1, N=length(OD600), Average=mean(OD600), StDev = sd(OD600))


# Reorder the levels of the 'Sample' variable
sMOI_1$Input <- factor(sMOI_1$Input, levels = c("Bacteria", "ANB28", "KB824", "SBP2Φ2", "Cocktail"))


#growth curve
moi1_gc <- ggplot(sMOI_1, aes(x=Time, y=Average, color = Input))+
  geom_ribbon(aes(ymin=Average-StDev, ymax = Average+StDev), fill = "#e3e3e3", linetype=0)+
  geom_line(size = 1.5) +
  scale_color_manual(values = c("black", "#FEC000", "#0420BC", "#B7167E", "#EF2402")) +
  labs(x="Time(Hours)", y ="OD600nm") +
  theme_classic()+
  theme(
    plot.title = element_text(size=20, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=20, face="bold"),
    axis.title.y = element_text(size=20, face="bold"), 
    axis.text.x = element_text(size=15), 
    axis.text.y = element_text(size=15), 
    legend.key.size = unit(1, 'cm'), #change legend key size
        legend.title = element_text(size=15), #change legend title font size
        legend.text = element_text(size=15))+ #change legend text font size) +
  xlim(1, 48) 
moi1_gc

# Reorder the levels of the 'Sample' variable
MOI_1_auc$Input <- factor(MOI_1_auc$Input, levels = c("Bacteria", "ANB28", "KB824", "SBP2Φ2", "Cocktail"))


moi1_anova_graph <- MOI_1_auc%>%
  ggplot(aes(x=factor(Input, level=c("Bacteria", "ANB28", "KB824", "SBP2Φ2", "Cocktail")), y=auc_l, fill = Input)) + 
  geom_violin() +
  geom_jitter() +
  labs(y = "AUC", x = "MOI") +
  theme_classic()+
  theme(
    plot.title = element_text(size=18, hjust = 0.5, face="bold"),
    axis.title.x = element_text(size=20, face="bold"),
    axis.title.y = element_text(size=20, face="bold"), 
    axis.text.x = element_text(size=15, angle = 45, hjust = 1), 
    axis.text.y = element_text(size=15), 
    legend.key.size = unit(1, 'cm'), #change legend key size
        legend.title = element_text(size=15), #change legend title font size
        legend.text = element_text(size=13))+ #change legend text font size) +
  stat_compare_means(method = "anova", label.y = 0) +
  scale_fill_manual(values = c("black", "#FEC000" , "#0420BC", "#B7167E", "#EF2402"))
moi1_anova_graph

```

```{r}
Cocktailfigure <- ggarrange(moi1_gc, moi1_anova_graph, 
                     labels = c("A", "B"),
                     common.legend = TRUE, legend = "bottom", 
                     align = "h", 
                     font.label = list(size = 18, face = "bold")) 

png('Figures/Cocktail.png', units="in", width=10, height=5, res=600)
Cocktailfigure
dev.off()
```

